A Computational Account of Default-Mode Function\\by Control Theory and Reinforcement Learning

### 2016-07-15 paper.tex
anat rtpj

relevance is the critical factor that determines whether an object activates the ventral network (Downar et al., 2001). The ventral network might be considered a prime candi-date for mediating orienting to salient but unimportant stimuli, i.e., exogenous attention (Posner and Cohen, 1984), be- cause under passive conditions it is highly responsive to distinctive sensory
events in all modalities (Downar et al., 2000). The ventral network is well activated by stimuli that are important, even if they are not very distinctive. 
CURRENT OPINION: VA network does underlie  stimulus-driven reorienting to environmental stimuli based on their task relevance. An important conclusion from these neuroimaging studies is that the psychological dis- tinction between exogenous and endogenous orienting (Jo- nides, 1981) may not map onto different neural systems.

>>>>

relevance is the critical factor that determines whether an object activates the ventral network (Downar et al., 2001). The ventral network might be considered a prime candi-date for mediating orienting to salient but unimportant stimuli, i.e., exogenous attention (Posner and Cohen, 1984), be- cause under passive conditions it is highly responsive to distinctive sensory
events in all modalities (Downar et al., 2000). The ventral network is well activated by stimuli that are important, even if they are not very distinctive. 
CURRENT OPINION: VA network does underlie  stimulus-driven reorienting to environmental stimuli based on their task relevance. An important conclusion from these neuroimaging studies is that the psychological dis- tinction between exogenous and endogenous orienting (Jo- nides, 1981) may not map onto different neural systems. "changing the control of behavior from one environ- mental input to another". Similar reorienting mechanisms may also be involved in shifting from a broad range of ‘‘internally directed’’ processes in order to deal with environmental events, as when interrupting memory retrieval (‘‘did I lock the car door?’’) to respond to a sudden stimulus (‘‘is that my cell phone ring- ing?’’). -> medites between the Default-Mode function and other more environmentally directed processing goals.
